EldersAIR: Main analysis - initial

### 2021-04-16 main_analysis_final.Rmd
New RMDs for main analysis

---
title: 'EldersAIR: Main analysis - initial'
author: "Ethan Walker"
date: "Started 31 March 2021; Updated 13 April 2021"
output: pdf_document
---

@@

```{r}
library(readxl)
library(naniar)
library(lubridate)
library(emmeans)
library(broom)
library(broom.mixed)
library(zoo)
library(car)
library(lme4)
library(lmerTest)
library(mctest)
library(tidyverse)
library(knitr)
library(kableExtra)
library(MASS)
library(faraway)
library(splines)
#library(DHARMa)
```

@@

treatments_blind <- rbind(treatments_blind_nn, treatments_blind_npt) %>% 
  mutate(home_id_num = as.factor(HomeID),
         treatment_blind = as.factor(CodedCondition),
         area = as.factor(area)) %>% 
  dplyr::select(area, home_id_num, treatment_blind)

@@

```{r}
## select outcome variable
### bp_sys, bp_dia, fvc, fev1, fev1_fvc_ratio, fvc_pp, fev1_pp, pm_mean_visit
analysis_data <- elders_cleaned_dataset_by_visit %>% 
  mutate(treatment = factor(treatment,
                            levels = c("Placebo", "Filter", "Education"),
                            labels = c("Placebo", "Filter", "Education")),
         visit_intervention_diff = round(difftime(sampling_date, intervention_date, 
                                            units = "days"), digits = 0),
         visit_intervention_diff = as.numeric(visit_intervention_diff),
         visit_intervention_diff = if_else(winter_id == 1, 9999,
                                           visit_intervention_diff)) %>% 
  mutate(outcome = bp_dia)  # select outcome here

# Prep data to run through the model
## calculate mean outcome per winter
## spread data to 1 row per adult - so Winter 1/baseline outcome is a covariate
analysis_data_1row <- analysis_data %>% 
  arrange(area, home, adult_id_char, winter_id, sampling_visit) %>% 
  group_by(area, adult_id_char, winter_id) %>% 
  mutate(mean_outcome = mean(outcome, na.rm = T)) %>% 
  ungroup() %>% 
  dplyr::select(area, home, adult_id_char, winter_id, sampling_visit, 
                cohort, treatment_blind, treatment, mean_outcome) %>% 
  distinct(area, adult_id_char, winter_id, .keep_all = T) %>% 
  group_by(area, adult_id_char) %>% 
  pivot_wider(names_from = "winter_id", values_from = "mean_outcome") %>% 
  mutate(mean_outcome = `2`,
         baseline_outcome = `1`) %>% 
  replace_with_na(replace = list(baseline_outcome = NaN, mean_outcome = NaN)) %>% 
  #filter(!is.na(mean_outcome)) %>% 
  ungroup()

analysis_data_2row_old <- analysis_data %>% 
  arrange(area, home, adult_id_char, winter_id, sampling_visit) %>% 
  mutate(outcome = outcome) %>% 
  dplyr::select(area, home, adult_id_char, winter_id, sampling_visit, 
                cohort, treatment_blind, treatment, outcome,
                visit_intervention_diff) %>% 
  group_by(area, adult_id_char, sampling_visit) %>% 
  pivot_wider(names_from = "winter_id", values_from = "outcome") %>% 
  arrange(area, home, adult_id_char, sampling_visit) %>% 
  mutate(outcome = `2`,
         baseline_outcome = `1`) %>% 
  replace_with_na(replace = list(baseline_outcome = NaN, outcome = NaN)) %>% 
  filter(!is.na(outcome) | !is.na(baseline_outcome)) %>% 
  ungroup()

@@

analysis_data_4row <- analysis_data %>% 
  arrange(area, home, adult_id_char, winter_id, sampling_visit) %>% 
  mutate(outcome = outcome,
         visit_intervention_diff = if_else(visit_intervention_diff == 9999, 0,
                                           visit_intervention_diff)) %>%  
  dplyr::select(area, home, adult_id_char, winter_id, sampling_visit, 
                cohort, treatment_blind, treatment, outcome,
                visit_intervention_diff)

@@

# Model Code - Data formatted as 1 row per person  
Using mean outcome per winter  
baseline_outcome = Winter 1  
mean_outcome = Winter 2  
```{r, echo=T}
itt_health_results_1row <- lmer(mean_outcome ~ treatment_blind + baseline_outcome + 
                                (1 | home:cohort:area),
                                data = analysis_data_1row)
```

```{r, eval=F}
isSingular(itt_health_results_1row)

summary(itt_health_results_1row)

tidy_results_1row <- tidy(itt_health_results_1row, conf.int = TRUE) %>% 
  mutate(group_filter = if_else(grepl("treatment", term), 1, 0)) %>% 
  filter(group_filter == 1) %>% 
  mutate(term = gsub("treatment_blind", "", term)) %>% 
  mutate(estimate = round((estimate), digits = 2),
         conf.low = round((conf.low), digits = 2),
         conf.high = round((conf.high), digits = 2)) %>% 
  dplyr::select(term, estimate, conf.low, conf.high, p.value) %>% 
  mutate(term = gsub("treatment", "", term),
         model = "1-row") %>% 
  dplyr::select(-p.value)
tidy_results_1row

plot(itt_health_results_1row, main = "ITT Primary Model", 
     xlab = "fitted values", ylab = "residuals")
qqnorm(residuals(itt_health_results_1row), main = "ITT Primary Model")
qqline(residuals(itt_health_results_1row))
```

# Model Code - Data formatted as 2 rows per person  
outcome = outcome from Winter 2 visits (up to 2 repeated measures)  
baseline_outcome = mean outcome from Winter 1  
Two ways of dealing with/looking at time since intervention:  
   visit_intervention_diff is days since intervention; included as numeric covariate  
   sampling_visit designates Visit 1 or Visit 2 of Winter 2; included as interaction term  
```{r, echo=T}
itt_health_results_2row <- lmer(outcome ~ treatment_blind + visit_intervention_diff + 
                                baseline_outcome + (1 | adult_id_char:home:cohort:area), 
                                data = analysis_data_2row)

# Or with interaction term for sampling visit

itt_health_results_2row_int <- lmer(outcome ~ treatment_blind*sampling_visit + 
                                    baseline_outcome + (1 | adult_id_char:home:cohort:area), 
                                    data = analysis_data_2row)
```

```{r, eval=F}
isSingular(itt_health_results_2row)

@@

int_emmeans <- emmeans(itt_health_results_2row_int, revpairwise ~ treatment | sampling_visit)

save_contrasts <- confint(int_emmeans$contrasts) %>% 
  mutate(estimate = round((estimate), digits = 2),
         conf.low = round((lower.CL), digits = 2),
         conf.high = round((upper.CL), digits = 2)) %>% 
  dplyr::select(contrast, sampling_visit, estimate, conf.low, conf.high) 
save_contrasts

@@

# Model Code - Data formatted as 4 rows per person  
This model doesn't adjust for baseline, but includes winter_id as an interaction term.  
Effect of the intervention is observed using the interaction contrasts for Winter 2.  
outcome = outcome from up to 4 visits from Winter 1 and Winter 2  
winter_id designates Winter 1 or Winter 2  
visit_intervention_diff is days since intervention; included as numeric covariate  
```{r, echo=T}
itt_health_results_4row <- lmer(outcome ~ treatment_blind*winter_id + visit_intervention_diff + 
                                (1 | adult_id_char:home:cohort:area), data = analysis_data_4row)
```

```{r, eval=F}
summary(itt_health_results_4row)

isSingular(itt_health_results_4row)

int_emmeans <- emmeans(itt_health_results_4row, revpairwise ~ treatment_blind | winter_id)

tidy_results_4row <- confint(int_emmeans$contrasts) %>% 
  mutate(estimate = round((estimate), digits = 2),
         conf.low = round((lower.CL), digits = 2),
         conf.high = round((upper.CL), digits = 2)) %>% 
  dplyr::select(contrast, winter_id, estimate, conf.low, conf.high) %>% 
  filter((contrast == "Filter - Placebo" | contrast == "Education - Placebo") & winter_id == 2) %>% 
  mutate(contrast = if_else(contrast == "Filter - Placebo", "Filter", "Education"),
         model = "4-row") %>% 
  rename(term = contrast) %>% 
  dplyr::select(-winter_id)
tidy_results_4row

plot(itt_health_results_4row, main = "ITT Primary Model", 
     xlab = "fitted values", ylab = "residuals")
qqnorm(residuals(itt_health_results_4row), main = "ITT Primary Model")
qqline(residuals(itt_health_results_4row))
```

```{r, eval=F}
# Print all model results for comparison

results_combined <- rbind(tidy_results_1row, tidy_results_2row, tidy_results_4row)

itt_pm_plot_estimates <- results_combined %>%
  mutate(model = factor(model,
                        levels = c("1-row", "2-row", "4-row"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "Model comparison for ITT framework") +
  labs(y = "Estimate compared to Control") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_pm_plot_estimates
```

```{r}
model_comparison_function <- function(data, outcome_var, var_name) {

analysis_data <- data %>% 
  mutate(treatment = factor(treatment,
                            levels = c("Placebo", "Filter", "Education"),
                            labels = c("Placebo", "Filter", "Education")),
         visit_intervention_diff = round(difftime(sampling_date, intervention_date, 
                                            units = "days"), digits = 0),
         visit_intervention_diff = as.numeric(visit_intervention_diff),
         visit_intervention_diff = if_else(winter_id == 1, 9999,
                                           visit_intervention_diff)) %>% 
  rename(outcome = outcome_var)  # select outcome here

analysis_data_1row <- analysis_data %>% 
  arrange(area, home, adult_id_char, winter_id, sampling_visit) %>% 
  group_by(area, adult_id_char, winter_id) %>% 
  mutate(mean_outcome = mean(outcome, na.rm = T)) %>% 
  ungroup() %>% 
  dplyr::select(area, home, adult_id_char, winter_id, sampling_visit, 
                cohort, treatment_blind, treatment, mean_outcome) %>% 
  distinct(area, adult_id_char, winter_id, .keep_all = T) %>% 
  group_by(area, adult_id_char) %>% 
  pivot_wider(names_from = "winter_id", values_from = "mean_outcome") %>% 
  mutate(mean_outcome = `2`,
         baseline_outcome = `1`) %>% 
  replace_with_na(replace = list(baseline_outcome = NaN, mean_outcome = NaN)) %>% 
  #filter(!is.na(mean_outcome)) %>% 
  ungroup()

itt_health_results <- lmer(mean_outcome ~ treatment_blind + baseline_outcome + 
                      (1 | home:cohort:area),
                      data = analysis_data_1row)

tidy_results_1row <- tidy(itt_health_results, conf.int = TRUE) %>% 
  mutate(group_filter = if_else(grepl("treatment", term), 1, 0)) %>% 
  filter(group_filter == 1) %>% 
  mutate(term = gsub("treatment_blind", "", term)) %>% 
  mutate(estimate = round((estimate), digits = 2),
         conf.low = round((conf.low), digits = 2),
         conf.high = round((conf.high), digits = 2)) %>% 
  dplyr::select(term, estimate, conf.low, conf.high, p.value) %>% 
  mutate(term = gsub("treatment_blind", "", term),
         model = "1-row") %>% 
  dplyr::select(-p.value)

itt_health_results2 <- lmer(outcome ~ treatment_blind + visit_intervention_diff + baseline_outcome + 
                      (1 | adult_id_char:home:cohort:area), data = analysis_data_2row)

tidy_results_2row <- tidy(itt_health_results2, conf.int = TRUE) %>% 
  mutate(group_filter = if_else(grepl("treatment", term), 1, 0)) %>% 
  filter(group_filter == 1) %>% 
  mutate(term = gsub("treatment_blind", "", term)) %>% 
  mutate(estimate = round((estimate), digits = 2),
         conf.low = round((conf.low), digits = 2),
         conf.high = round((conf.high), digits = 2)) %>% 
  dplyr::select(term, estimate, conf.low, conf.high, p.value) %>% 
  mutate(term = gsub("treatment_blind", "", term),
         model = "2-row") %>% 
  dplyr::select(-p.value)

analysis_data_4row <- analysis_data %>% 
  arrange(area, home, adult_id_char, winter_id, sampling_visit) %>% 
  mutate(outcome = outcome,
         visit_intervention_diff = if_else(visit_intervention_diff == 9999, 0,
                                           visit_intervention_diff)) %>%  
  dplyr::select(area, home, adult_id_char, winter_id, sampling_visit, 
                cohort, treatment_blind, treatment, outcome,
                visit_intervention_diff)

itt_health_results3 <- lmer(outcome ~ treatment_blind*winter_id + visit_intervention_diff + 
                      (1 | adult_id_char:home:cohort:area), data = analysis_data_4row)

int_emmeans <- emmeans(itt_health_results3, revpairwise ~ treatment_blind | winter_id)

tidy_results_4row <- confint(int_emmeans$contrasts) %>% 
  mutate(estimate = round((estimate), digits = 2),
         conf.low = round((lower.CL), digits = 2),
         conf.high = round((upper.CL), digits = 2)) %>% 
  dplyr::select(contrast, winter_id, estimate, conf.low, conf.high) %>% 
  filter((contrast == "Queso - Guac" | contrast == "Salsa - Guac") & winter_id == 2) %>% 
  mutate(contrast = if_else(contrast == "Queso - Guac", "Queso", "Salsa"),
         model = "4-row") %>% 
  rename(term = contrast) %>% 
  dplyr::select(-winter_id)

results_combined <- rbind(tidy_results_1row, tidy_results_2row, tidy_results_4row)

itt_pm_plot_estimates <- results_combined %>%
  mutate(model = factor(model,
                        levels = c("1-row", "2-row", "4-row"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "Model comparison for ITT framework", subtitle = var_name) +
  labs(y = "Estimate compared to Guac") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 14), 
          axis.text.x = element_text(size = 14, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 14, colour = "black"),
          axis.title.y = element_text(size = 14,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_pm_plot_estimates

}

## select outcome variable
### bp_sys, bp_dia, fvc, fev1, fev1_fvc_ratio, fvc_pp, fev1_pp, pm_mean_visit
```

\pagebreak

```{r}
model_comparison_function(elders_cleaned_dataset_by_visit, "bp_sys", "Systolic BP")
```

\pagebreak

```{r}
model_comparison_function(elders_cleaned_dataset_by_visit, "bp_dia", "Diastolic BP")
```

\pagebreak

```{r}
model_comparison_function(elders_cleaned_dataset_by_visit, "fvc", "FVC")
```

\pagebreak

```{r}
model_comparison_function(elders_cleaned_dataset_by_visit, "fev1", "FEV1")
```

\pagebreak

```{r}
model_comparison_function(elders_cleaned_dataset_by_visit, "fvc_pp", "FVC Percent Predicted")
```

\pagebreak

```{r}
model_comparison_function(elders_cleaned_dataset_by_visit, "fev1_pp", "FEV1 Percent Predicted")
```

\pagebreak

```{r}
model_comparison_function(elders_cleaned_dataset_by_visit, "fev1_fvc_ratio", "FEV1/FVC Ratio")
```

\pagebreak

# Interpretation and next steps

All of the model frameworks give similar results across all outcomes that were assessed.  
I am inclined to use the 2nd framework as the primary model (up to 2 rows of data per person).  
This model is a nice compromise between the 1-row and 4-row data. The 
confidence intervals are smaller than the models with 4-row data - even a bit smaller 
than the models with the 1-row data- and the repeated measures allow you to include 
an interaction term for visit number to look at the effect of time since the intervention.

Next steps will be to evaluate diagnostic plots and potential outliers using the 
final model framework. I am also working on a Table 1 for NN and NPT areas separately, 
as well as a table that compares covariates between those who did/did not miss a 
visit or winter of follow-up.

>>>>

---
title: 'EldersAIR: Main analysis - final version and manuscript results'
author: "Ethan Walker"
date: "Started 16 April 2021; Updated 16 April 2021"
output: pdf_document
---

@@

```{r}
library(readxl)
library(naniar)
library(lubridate)
library(emmeans)
library(broom)
library(broom.mixed)
library(zoo)
library(car)
library(lme4)
library(lmerTest)
library(mctest)
library(tidyverse)
library(knitr)
library(kableExtra)
#library(MASS)
library(faraway)
library(splines)
library(influence.ME)
```

@@

treatments_blind <- rbind(treatments_blind_nn, treatments_blind_npt) %>% 
  mutate(home_id_num = as.factor(HomeID),
         treatment_blind = as.factor(CodedCondition),
         area = as.factor(area)) %>% 
  select(area, home_id_num, treatment_blind)

@@

```{r}
## select outcome variable
### bp_sys, bp_dia, fvc, fev1, fev1_fvc_ratio, fvc_pp, fev1_pp, pm_mean_visit
analysis_data <- elders_cleaned_dataset_by_visit %>% 
  mutate(treatment = factor(treatment,
                            levels = c("Placebo", "Filter", "Education"),
                            labels = c("Placebo", "Filter", "Education")),
         visit_intervention_diff = round(difftime(sampling_date, intervention_date, 
                                            units = "days"), digits = 0),
         visit_intervention_diff = as.numeric(visit_intervention_diff),
         visit_intervention_diff = if_else(winter_id == 1, 9999,
                                           visit_intervention_diff)) %>% 
  mutate(outcome = fev1)  # select outcome here

@@

@@

# ITT Model Code - Data formatted as 2 rows per person  
outcome = outcome from Winter 2 visits (up to 2 repeated measures)  
baseline_outcome = mean outcome from Winter 1  
Two ways of dealing with/looking at time since intervention:  
   visit_intervention_diff is days since intervention; included as numeric covariate  
   sampling_visit designates Visit 1 or Visit 2 of Winter 2; included as interaction term  
```{r, echo=T}
itt_health_results_2row <- lmer(outcome ~ treatment_blind + visit_intervention_diff + 
                                baseline_outcome + (1 | adult_id_char:home:cohort:area), 
                                data = analysis_data_2row)

isSingular(itt_health_results_2row)

@@

@@

# ITT primary model identify potential influential datapoints
```{r}
influential <- influence(itt_health_results_2row, obs = TRUE)
cooks <- cooks.distance.estex(influential, sort = TRUE)
plot.estex(influential, which = "cook")

# bp_sys: try removing lines 127, 202, 95, 32, 48, 31, 17, 216, 128, 4
# bp_dia: try removing lines 42, 95, 192, 127, 48, 202, 191, 31, 223, 7
# fvc: try removing lines 93, 94, 34, 82, 35, 164, 142, 81, 219, 32
# fev1: try removing lines 79, 34, 24, 80, 25, 82, 26, 230, 5, 6
# fev1_fvc_ratio: try removing lines
# fvc_pp: try removing lines
# fev1_pp: try removing lines
```

# ITT Effect modification model code
```{r}
itt_health_results_2row_int <- lmer(outcome ~ treatment_blind*sampling_visit + 
                                    baseline_outcome + (1 | adult_id_char:home:cohort:area), 
                                    data = analysis_data_2row)
```

### 2021-04-16 main_analysis_initial.Rmd
New RMDs for main analysis

---
title: 'EldersAIR: Main analysis - initial'
author: "Ethan Walker"
date: "Started 31 March 2021; Updated 13 April 2021"
output: pdf_document
---

@@

```{r}
library(readxl)
library(naniar)
library(lubridate)
library(emmeans)
library(broom)
library(broom.mixed)
library(zoo)
library(car)
library(lme4)
library(lmerTest)
library(mctest)
library(tidyverse)
library(knitr)
library(kableExtra)
library(MASS)
library(faraway)
library(splines)
#library(DHARMa)
```

@@

@@

itt_health_results_2row_int <- lmer(outcome ~ treatment_blind*sampling_visit + 
                                    baseline_outcome + (1 | adult_id_char:home:cohort:area), 
                                    data = analysis_data_2row)
```

@@

>>>>

---
title: 'EldersAIR: Main analysis - initial'
author: "Ethan Walker"
date: "Started 31 March 2021; Updated 14 April 2021"
output: pdf_document
---

@@

```{r}
library(readxl)
library(naniar)
library(lubridate)
library(emmeans)
library(broom)
library(broom.mixed)
library(zoo)
library(car)
library(lme4)
library(lmerTest)
library(mctest)
library(tidyverse)
library(knitr)
library(kableExtra)
#library(MASS)
library(faraway)
library(splines)
```

@@

analysis_data_2row_diff <- analysis_data %>% 
  arrange(area, home, adult_id_char, winter_id, sampling_visit) %>% 
  group_by(area, home, adult_id_char, winter_id) %>% 
  mutate(outcome = if_else(winter_id == 1, mean(outcome, na.rm = T), outcome)) %>% 
  dplyr::select(area, home, adult_id_char, winter_id, sampling_visit, 
                cohort, treatment_blind, treatment, outcome,
                visit_intervention_diff) %>% 
  group_by(area, adult_id_char) %>% 
  pivot_wider(names_from = "winter_id", values_from = "outcome") %>% 
  arrange(area, home, adult_id_char, sampling_visit) %>% 
  mutate(outcome = `2`,
         baseline_outcome = `1`,
         baseline_outcome = if_else(is.na(baseline_outcome), first(baseline_outcome),
                                    baseline_outcome)) %>% 
  replace_with_na(replace = list(baseline_outcome = NaN, outcome = NaN)) %>% 
  filter(visit_intervention_diff != 9999) %>% 
  mutate(outcome_diff = outcome - baseline_outcome) %>% 
  ungroup()

@@

itt_health_results_2row_int <- lmer(outcome ~ treatment_blind*sampling_visit + 
                                    baseline_outcome + (1 | adult_id_char:home:cohort:area), 
                                    data = analysis_data_2row)

# Or with difference between Winter 2 visit and mean baseline as the outcome
## This is not an ideal model due to the imbalance of our data at baseline
## Difference measures will not deal with regression to the mean like adjusting for baseline

itt_health_results_2row_diff <- lmer(outcome_diff ~ treatment_blind + visit_intervention_diff + 
                                    (1 | adult_id_char:home:cohort:area), 
                                    data = analysis_data_2row_diff)
```

@@

isSingular(itt_health_results_2row_diff)

summary(itt_health_results_2row_diff)

tidy_results_2row_diff <- tidy(itt_health_results_2row_diff, conf.int = TRUE) %>% 
  mutate(group_filter = if_else(grepl("treatment", term), 1, 0)) %>% 
  filter(group_filter == 1) %>% 
  mutate(term = gsub("treatment_blind", "", term)) %>% 
  mutate(estimate = round((estimate), digits = 2),
         conf.low = round((conf.low), digits = 2),
         conf.high = round((conf.high), digits = 2)) %>% 
  dplyr::select(term, estimate, conf.low, conf.high, p.value) %>% 
  mutate(term = gsub("treatment", "", term),
         model = "2-row") %>% 
  dplyr::select(-p.value)
tidy_results_2row_diff
